\documentclass[General-Information/editedlog.tex]{subfiles}
\begin{document}
\begin{question}
    Do islands exist?
\end{question}

\begin{question}
    What happens when you run the algorithm when setting a contractible Reeb height to 0? What does this look like geometrically? Zero Resolution.
\end{question}

\begin{question}
    How to knot filter? \\
    Seems like you can just filter by the disks your flooding, but maybe there's a way to resolve geometrically to get another knot. (See \href{http://www.math.titech.ac.jp/~kalman/cobordism-talk.pdf}{here})
\end{question}



\begin{question}

Can we list all of the possible orderings of Reeb heights?
\end{question}

\begin{question}

Can we do a bunch of examples of computing persistent LCH?
\end{question}

\begin{question}
When we have classes with multiple elements we can sometimes swap the orders. If we take the Reeb heights after swapping, how does this change persistent LCH (examples)?
\end{question}

\begin{question}
Are finite intervals invariant under legandrian isotopy?
\end{question}
\begin{proof}[Answer]
    No! That should be apart of our persistent equivalence relation.
\end{proof}

\begin{question}
Double shading corresponds to contractible, extras are stupid contractible.
\end{question}
\begin{proof}[Answer]
    See \ref{prop:contractdesc} (\TODO restate prop to include the fact that extras and double shaders are always contractible).
\end{proof}

\begin{question}
Could we prove that the algorithm finishing is preserved through isotopy by considering the equations under stable tame isomophism?
\end{question}

\begin{question}
Could we use grid projection to prove things?
\end{question}

\begin{question}
Make a python script to compute height assignments.
\end{question}
\begin{proof}[Answer]
    More or less done thanks to Maya.
\end{proof}

\begin{question}
Is non-switchability a property of only having two classes.
\end{question}

\begin{question}
We should call this the flooding algorithm - knot is flooded  - each class is a "tier" 
\end{question}
\begin{proof}[Answer]
    Yes.
\end{proof}

\begin{question}

Work flow:



Draw knot in plat position, get generators

Ask for z-graded differential

Compute height assignments with python

\end{question}

\begin{question}
    What would the term super (stupid) contractible even mean? The maximal number of contractible chords you can simultaneously set to zero is a well defined number, but there may be multiple collections that achieve this maximum. This probably isn't a knot invariant, but also probably interesting to look into. Where do our extras from our algorithm lie in this picture? Certainly the number of super contractibles is greater than or equal
\end{question}

\begin{question}
    When drawing the bar-code, which generator or sums of generators should we use? In some cases it seems that it is ambiguous and we have a choice of which generators to use, and each choice leads to different effects when the heights of certain generators are changed.
\end{question}

\begin{question}
Hypothesis, when changing the height of one generator, it will affect the bar-code only by moving the birth and death time of certain lines, rather than by introducing additional lines.
\end{question}

\begin{question}
How will the bar-code be affected by Reidemeister moves (i.e. under the addition of new generators)?
\end{question}

If R3 prevents any augmentation from existing.

\begin{question}
    Game plan:
        \begin{enumerate}
            \item (John) What isomorphisms are induced by Reidemiester moves.
            \item (John) (last on list) Figure out quasi-isomorphism for linearized LCH. Need to relate augmentations.
            \item (John) Find valid Lagranian moves to show isotopy in Lagrangian projeciton.
        \end{enumerate}
\end{question}
Generic stable tame isomorphism destroys the bar code structure. Need to restrict the knot moves. Hard problem is figure out the valid stable tame isomorphisms coming from knot moves. If a generator is not homologically essential, then it should be finite and furthermore contractible and can be made arbitrarily small. Can we move a bar of finite length past the birth of an infinite bar (what if birth and death happens in-between the birth of inifinite length bar too). Can delete bars of length epsilon where epsilon can be made small. Not all finite bars. The bad case can all be finite bars are "contractible."

Differential decreases height and degree. (John) Need to figure degrees from triple point move. Also find valid lagrangian reidemeister moves.

Extras from Row Operations.

Translation vs contracting the finite bar. Proper heights is the stuff born or dying in between the bar's length, is this an invariant of isotopy?
\end{document}
